Radial Velocity Upper Limits on Planets around Radio Exoplanet Candidates GJ~1151 and GJ~412A

### 2019-02-28 paper/ms.tex
shimwell

@@

Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey (LoTSS) with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations. But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced. Based on this restricted cross-match, Vedantham et al. (submitted) and Callingham et al. (submitted) have detected the red dwarfs GJ~1151 and GJ~412A \citep[M1.0:][]{} respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.

@@

The results of this analysis conclusively rule out binary companions or planets on short orbits more massive than Neptune as the origin of the radio signals from GJ~1151 and GJ~412A. We nevertheless cannot rule out in either case planets less massive than a few Earth masses. Given that Vedantham et al. (submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the planet hypothesis remains reasonable.

>>>>

\author[0000-0001-5648-9069]{Timothy W. Shimwell}
\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Oude Hoogeveensedijk 4, Dwingeloo, 7991 PD, The Netherlands}

@@

Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey \citep[LoTSS:][]{lotss} with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations. But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced. Based on this restricted cross-match, Vedantham et al. (submitted) and Callingham et al. (submitted) have detected the red dwarfs GJ~1151 and GJ~412A \citep[M1.0:][]{} respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.

@@

The results of this analysis conclusively rule out binary companions or planets on short orbits more massive than Neptune as the origin of the radio signals from GJ~1151 and GJ~412A. We nevertheless cannot rule out in either case planets less massive than a few Earth masses. Given that Vedantham et al. (submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the planet hypothesis remains reasonable. Because both targets are so red, to achieve significantly higher precision than attained by HIRES or HARPS would require moving to the infrared, using one of the IR precision RV instruments currently being commissioned, such as the Habitable-zone Planet Finder \citep[HPF:][]{hpf}.
